Milestone 2: Scoring Algorithms Test

### 2019-10-31 perf_release_criteria/milestone_3/ms_2_scoring_algo_analysis.Rmd
Creating new `milestone 3` directory for analysis.

---
title: 'Milestone 2 Test: Scoring Algorithms'
output:
  html_document:
    df_print: paged
---

@@

```{r data_load, echo=FALSE}
load('data/milestone2/analysis_10022019_corr.RData')
```

>>>>

---
title: 'Milestone 2: Scoring Algorithms Test'
output:
  html_notebook:
    theme: cosmo
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
---

@@

```{r data_load, echo=FALSE}
load('../data/milestone2/analysis_10022019_corr.RData')
```
